Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data

### 2015-06-22 Presentations/Dinamica de Vetores-SP-2015/dengueARS0.tex

@@

\begin{frame}
\frametitle{\rr's Uncertainty}
\begin{center}
\begin{figure}
  \includegraphics[width=9cm]{./rt_series.png}
\end{figure}
\end{center}
\end{frame}
\subsection{Vector dynamics}
\begin{frame}
\frametitle{Environmental determinants}
\begin{itemize}[<+->]
 \item A. Aegypti population dynamics display marked seasonality
 \item Temperature, Humidity and rainfall are important factors
 \item Environmental stock of eggs
 \item Effects on mosquito reproduction are non-linear
 \item Delayed influence
\end{itemize}

@@

\end{frame}
\begin{frame}
 \frametitle{Collaboration possibilities}
 \begin{itemize}
  \item Relaxing other simplifying assumptions in classical epidemiological 
models.
\item Looking into modeling spatio-temporal dynamics taking into account 
Environmental stock of eggs.
\item Separating noise from relevant varibility in observational data, and 
finding new ways of integrating it into models.
 \end{itemize}

\end{frame}
\begin{frame}

>>>>

\subsection{Vector dynamics}

\begin{frame}
\frametitle{Environmental determinants}
\begin{block}{Vector dynamics}
\begin{itemize}[<+->]
 \item A. Aegypti population dynamics display marked seasonality
 \item Temperature, Humidity and rainfall are important factors
 \item Environmental stock of eggs
 \item Effects on mosquito reproduction are non-linear
 \item Delayed influence
\end{itemize}
\end{block}

@@

\begin{frame}
\frametitle{\rr's Uncertainty}
\begin{center}
\begin{figure}
  \includegraphics[width=9cm]{./rt_series.png}
\end{figure}
\end{center}
\end{frame}

@@

\end{frame}
% \begin{frame}
%  \frametitle{Collaboration possibilities}
%  \begin{itemize}
%   \item Relaxing other simplifying assumptions in classical epidemiological 
% models.
% \item Looking into modeling spatio-temporal dynamics taking into account 
% Environmental stock of eggs.
% \item Separating noise from relevant varibility in observational data, and 
% finding new ways of integrating it into models.
%  \end{itemize}
% 
% 
% \end{frame}
\begin{frame}
